Improving Multi-Domain Neural Machine Translation with Differential Data Selection

### 2021-02-01 2021/acl-ijcnlp2021/mdmt.tex
started related work, more refs

\fyTodo{Label or covariate shift ?}
This problem is often approached with instance selection or reweighting strategies, where the available training data is used in proportion to its relevance for the chosen test conditions. Finding the optimal balance of training data is however a challenging task due for instance to similarity between domains / languages; it may also be suboptimal, as some domains or languages might be easier to train than others. Several recent proposals \cite{Wang17instance,Kumar19reinforcement, Wang20learning-multi} have explored ways to instead consider dynamic data selection strategy. We study in this contribution the proposal of \cite{Wang20balancing}, initially introduced for multilingual MT, with the goal to evaluate its potential in various single domain and multi-domain adaptation settings and assess DDS as an effective replacement to standard heuristics approaches.

@@

\cite{Wang20multidomain} for multidomain DA.

>>>>

\fyTodo{Label or covariate shift ?}
This problem is often approached with \emph{static} instance selection or re-weighting strategies, where the available training data is used in proportion to its relevance for the chosen test conditions. Finding the optimal balance of training data is however a challenging task due for instance to similarity between domains / languages, but also due to regularization effects of out-of-domain data; it may also be suboptimal, as some domains or languages might be easier to train than others. Several recent proposals \cite{Wang17instance,Kumar19reinforcement,Wang20learning-multi} have explored ways to instead consider \emph{dynamic} data selection strategy. We study in this contribution the proposal of \cite{Wang20balancing}, initially introduced for multilingual MT, with the goal to evaluate its potential in various single domain and multi-domain adaptation settings and assess DDS as an effective replacement to standard heuristics approaches.

@@

\cite{Wang20multidomain} adapts curriculum learning \cite{BengioXX} for multi-domain adaptation, where an optimal instance weighting scheme is found using Bayesian optimization techniques.

Also \cite{Saunders19adaptive}.
